### 2022-08-04 main/chapter_2ljets.tex
improve pruning footnote

\paragraph{Contours}
Exclusion contours, which are displayed in
Figures~\ref{fig:2ljets_contours_c1n2} and~\ref{fig:2ljets_contours_gmsb},
derive from fits with models that extend the background-only model with
additive signal samples.
To reduce the computational cost of building the hundreds of models%
\footnote{%
This is worded precisely. The dominant cost was not in fitting the models, nor
in histogramming the data (thanks to histogram caching), but in forming the
HistFactory model from those histograms.
I do not know why that model-building step took days of computer time per
model, but it did reduce to only hours after upgrading the \histfitter\ version
from \textsc{v0.64.0} to \textsc{v0.66.0}.
}%
across these grids, we prune the number of small irrelevant parameters
with \histfitter's pruning~\cite{histfittergithub} mechanism in ``method 2''.
This pruning method removes variations if the difference between their up and
down values do not exceed a threshold.
With pruning enabled, its default threshold is set to $1\%$ (relative to the
central yield), but to reduce its impact we use a threshold of $0.1\%$.
Validation studies comparing each of these pruning thresholds, against the
un-pruned version, and against a custom pruning implemented by myself, found no
significant differences.%
\footnote{%
Pruning is, however, the reason the signal patches (differences from
background-only to signal) in our serialized \hepdata\ models are so large;
they implement many small changes due to different decisions made by the
pruning implementation.
}

>>>>

\paragraph{Contours}
Exclusion contours, which are displayed in
Figures~\ref{fig:2ljets_contours_c1n2} and~\ref{fig:2ljets_contours_gmsb},
derive from fits with models that extend the background-only model with
additive signal samples.
To reduce the computational cost of building the hundreds of models%
\footnote{%
This is worded precisely. The dominant cost was not in fitting the models, nor
in histogramming the data (thanks to histogram caching), but in forming the
HistFactory model from those histograms.
I do not know why that model-building step took days of computer time per
model, but it did reduce to only hours after upgrading the \histfitter\ version
from \textsc{v0.64.0} to \textsc{v0.66.0}.
}%
across these grids, we prune the number of small irrelevant parameters
with \histfitter's pruning~\cite{histfittergithub} mechanism in ``method 2''.
This pruning method removes variations if the difference between their up and
down values do not exceed a threshold.
With pruning enabled, its default threshold is set to $1\%$ (relative to the
central yield), but to reduce its impact we use a threshold of $0.1\%$.
Validation studies comparing each of these pruning thresholds, against the
un-pruned version, and against a custom pruning implemented by myself, found no
significant differences.%
\footnote{%
Pruning is, however, the reason our signal patches (that describe differences
from background-only to signal models) in our serialized \hepdata\ models are
so large; they implement many small changes due to different decisions made by
the pruning algorithm.
}
